Project
========================================================


```{r  echo=FALSE, results='hide',message=FALSE}
library(caret)
```
**Reading and Processing the Data**

First: Reading the csv file, and look at the name of its variable
and Remove variables that are nulls

```{r  echo=FALSE, results='hide'}

```{r}
nullstrings=c("","NA")
data = read.csv("pml-training.csv", na.strings=nullstrings)
whichcolsarenull<-apply(data, 2, function(curcol){sum(is.na(curcol))})
Finaldata<-data[,which(whichcolsarenull==0)]
dim(Finaldata)
```
Column with mostly Nulls are removed
```{r echo=FALSE, results='hide',message=FALSE}
na.strings=c("NA","")
NULLS<-apply(data,2,function(x) {sum(is.na(x))})
Finaldata<-data[,which(NULLS==0)]
dim(Finaldata)
```
Also, The first 7 variables need to be removed since they are not related to the result. 
```{r}
Finaldata = Finaldata[,-c(1:7)]
dim(Finaldata)
```
**Data Partition**

Partitioning data into Training, and Testing set

```{r}
inTrain=createDataPartition(Finaldata$classe,p=0.7,list=FALSE)
training=Finaldata[-inTrain,]
testing=Finaldata[inTrain,]
dim(training);dim(testing)
```
**Building the Model**

*using random forest to build the model*

```{r cache=TRUE}
modelFit <- train(training$classe ~ ., data=training, method='rf',  trControl = trainControl(method = "cv", number = 4), allowParallel=T)
```

**Checking the accuracy of the model (in-sample error)**
The model is expected to be accurate , and using the model Fit, the accuracy was 1
```{r}
modelFit
```

**Using the model on testing data to predict its classe**
```{r}
pre<-predict(modelFit,testing)
```
**Testing the Model on CrossValidation Test by:**

    *Estimating the out-of-sample error using Confusion matrix*

```{r}
confusionMatrix(testing$classe,pre)
```
